Rethinking Felony Disenfranchisement: The Case of New York City and Miami

### 2019-05-08 markdown/kmorris_thesis.Rmd
Map wasn't working for lost voters on parole. Correct, run through

These individuals are identified by matching Department of Corrections and Community Supervisions data to the voter file using the methodology developed by Burch [-@Burch2010; -@Burch2011]. I use first, middle, and last names, and dates of birth, to join these two datasets.^[Matching on first and last names and dates of birth can result in false positive matches, especially in large states like New York. Following @Meredith2013, I report estimates of the potential impact of these false positives in the Appendix.] Figure \ref{fig:citymap} shows where these lost voters lived before going to prison (and city council districts).

```{r citywide-map, echo = FALSE, message = F, warning = F, fig.width = 5, fig.height = 5, fig.cap = "\\label{fig:citymap}Individuals Incarcerated in 2017 Who Voted Between 2007 and 2016", out.extra = '', fig.pos = "H", fig.align = "center"}
j <- readRDS("./output/city_map.RDS")
print(j)
```
The spatial concentration of lost

>>>>

These individuals are identified by matching Department of Corrections and Community Supervisions data to the voter file using the methodology developed by Burch [-@Burch2010; -@Burch2011]. I use first, middle, and last names, and dates of birth, to join these two datasets.^[Matching on first and last names and dates of birth can result in false positive matches, especially in large states like New York. Following @Meredith2013, I report estimates of the potential impact of these false positives in the Appendix.] Figure \ref{fig:citymap} shows where these lost voters lived before going to prison (and city council districts). There were ```r comma(sum(readRDS("./temp/disen_by_bg.rds")$lost_voters))``` such lost voters within New York City as of the 2017 general election, and ```r comma(nrow(readRDS("./temp/matched_ids_in_17.rds")))``` statewide.

```{r citywide-map, echo = FALSE, message = F, warning = F, fig.width = 5, fig.height = 5, fig.cap = "\\label{fig:citymap}Lost Voters on Election Day, 2017", out.extra = '', fig.pos = "H", fig.align = "center"}
j <- readRDS("./output/city_map.RDS")
print(j)
```
The spatial concentration of lost
